Paper_Figures

### 2019-12-09 analysis/PaperFigures.Rmd
overdue update

getStat = function(dat, stat, offset = 25000){
  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
  val = max(abs(unlist(dat[,stat])), na.rm = T)
  return(val)
  }

@@

getDims = function(dat, y.metric = "fst", offset = 100000){
  # dat = data.frame("mid" = mid, "fst" = febugst)
  peak = tryCatch({
    auc(dat$mid, unlist(abs(dat[,y.metric])), from = 500000 - offset, to = 500000 + offset)}
    , error = function(e){
      return(-9)
    })
  return(peak)
}

@@

getStat = function(dat, stat, offset = 25000){
  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
  val = max(abs(unlist(dat[,stat])), na.rm = T)
  return(val)
  }

wrapEHH = function(files){
  all.sum = data.frame()
  for(i in 1:length(files)){
    print(files[i])
    dat = read.csv(files[i])
    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, dom, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
    all.sum = rbind(all.sum, dat.sum)
    remove(dat)
  }
  return(all.sum)
}

@@

#Figure 1A left
dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c(0, 0.5, 1)) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

@@

#Figure 2C
```{r}
ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "IHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "IHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-c(data)) %>% unnest()

@@

kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

@@

#Combined AUC and MaxValue
kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

#Figure 2E
```{r}
ds = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Tajima.D_1 = abs(Tajima.D_1), Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

@@

MS6.1 = ms2b %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))

MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("TajD", "Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

@@

#Recessive
kkk.1b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points.b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

@@

#Combined AUC and MaxValue
kkk.3b %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))

#Dominant
kkk.1c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points.c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, TajD, ZengsE, FayWuH, Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

@@

#Combined AUC and MaxValue
kkk.3c %>% filter(variable %in% c("sim_ploidy", "sampGen", "TajD", "Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("TajD", "Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("TajD", "Fst", "iHS", "XPEHH"),], aes(y = value), shape = 18, color = "blue", position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

Supplemental Figure 
```{r}

lCV <- function(data, N = 1000, n = 50){
    aa = foreach(i = 1:N, .combine = rbind) %do% {
      ndat = sample(data, n)
      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
    return(quantile(aa,0.05, na.rm=T))
}

uCV <- function(data, N = 1000, n = 50){
    aa = foreach(i = 1:N, .combine = rbind) %do% {
      ndat = sample(data, n)
      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
    return(quantile(aa,0.95, na.rm=T))
}

pardir = "..." #Set directory housing data for SuppFig6
ehh = read.csv(paste(pardir, "rehh_calcs_SuppFig6.csv", sep = ""))

>>>>

@@

getDims = function(dat, y.metric = "fst", offset = 100000){
  # dat = data.frame("mid" = mid, "fst" = febugst)
  x = 1
  if(y.metric=="Tajima.D_1"){x = -1}
  peak = tryCatch({
    auc(dat$mid, unlist(x*(dat[,y.metric])), from = 500000 - offset, to = 500000 + offset)}
    , error = function(e){
      return(-9)
    })
  return(peak)
}

@@

getStat = function(dat, stat, offset = 25000){
  x = 1
  if(stat=="Tajima.D_1"){x = -1}
  dat = dat %>% filter(mid > 500000 - offset & mid < 500000 + offset)
  val = max(x*(unlist(dat[,stat])), na.rm = T)
  return(val)
  }

wrapEHH = function(files){
  all.sum = data.frame()
  for(i in 1:length(files)){
    print(files[i])
    dat = read.csv(files[i])
    dat.sum = dat %>% mutate(traj_ploidy = as.numeric(str_replace(traj_ploidy, "tp","")), sim_ploidy = as.numeric(str_replace(sim_ploidy, "sp","")), dom = as.numeric(str_replace(dom, "do","")), s = as.numeric(str_replace(s, "se","")), N = as.numeric(str_replace(N, "NN","")), mu = as.numeric(str_replace(mu, "mu","")), recomb = as.numeric(str_replace(recomb, "re","")), sampGen = as.numeric(str_replace(sampGen, "sG","")), fuseGen = as.numeric(str_replace(fuseGen, "fG","")), rep = as.numeric(str_replace(rep, "rep", ""))) %>% filter(!is.na(xpehh.p)) %>% mutate(mid = POSITION) %>% nest(-c(sim_ploidy, dom, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-data) %>% unnest()
    all.sum = rbind(all.sum, dat.sum)
    remove(dat)
  }
  return(all.sum)
}

@@

#Figure 1A left
dat1 %>% filter(ploidy %in% c(2, 4, 8) & dom %in% c("recessive", "additive", "dominant")) %>% ggplot(., aes(x=gen, y=freq, linetype=as.factor(dom), color=as.factor(ploidy))) + geom_line(size = 1.2) + scale_color_manual(name = "Ploidy", values = c("#F8766D", "#00BA38", "#619CFF")) + scale_linetype_manual(name = "Dominance", labels=c("Dominant", "Additive", "Recessive"), values = c("dashed", "solid", "dotted")) + xlim(0,500) + theme_bw() + xlab("Generation") + ylab("Allele Frequency") + theme(axis.text.y=element_text(size=16), axis.title.y=element_text(size=18),axis.text.x=element_text(size=16),axis.title.x=element_text(size=18),legend.text = element_text(size=16), legend.title = element_text(size=18))

@@

#Figure 2C
```{r}
ff = rehh %>% filter(!is.na(xpehh.p) & sampGen!=1000) %>% mutate(mid = POSITION) %>% nest(-c(s, dom, recomb, N, mu, sim_ploidy, traj_ploidy, sampGen, fuseGen, rep)) %>% mutate(size.xp = map(data, ~getDims(., y.metric = "XPEHH")), size.xp.p = map(data, ~getDims(., y.metric = "xpehh.p")), med.xp = map(data, ~getStat(., "XPEHH")), med.xpp = map(data, ~log(getStat(., "xpehh.p"))), size.ihs = map(data, ~getDims(., y.metric = "iHS")), size.ihs.p = map(data, ~getDims(., y.metric = "ihs.p")), med.ihs = map(data, ~getStat(., "iHS")), med.ihs.p = map(data, ~log(getStat(., "ihs.p")))) %>% select(-c(data)) %>% unnest()

@@

kkk.1 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2 = kkk %>% filter(dom == 0.5 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Std.Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "iHS" = size.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

@@

#Combined AUC and MaxValue
kkk.3 %>% filter(variable %in% c("sim_ploidy", "sampGen", "-TajD", "Std.Fst", "iHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("-TajD", "Std.Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = abs(value) / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH"),], aes(y = value, color = as.factor(sampGen)), shape = 18, position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ geom_point(data = kkk.med.points[kkk.med.points$variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH"),], aes(y = value), shape = 5, color = "black", position = position_dodge(width = 0.75), show.legend = F, size=2)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2"))+scale_color_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

#Figure 2E
```{r}
ds = ms2 %>% group_by(sim_ploidy, DS, rep, dom) %>% mutate(Div = mean(Pi.2) - Pi.1, Fst = scale(fst)) %>% ungroup() %>% nest(-c(sim_ploidy, dom, DS, rep)) %>% mutate(size.div = map(data, ~getDims(., y.metric = "Div")), size.taj = map(data, ~getDims(., y.metric = "Tajima.D_1")), size.h = map(data, ~getDims(., y.metric = "Fay.Wu.H_1")), size.e = map(data, ~getDims(., y.metric = "Zeng.E_1")), size.fst = map(data, ~getDims(., y.metric = "Fst")), size.dxy = map(data, ~getDims(., y.metric = "dxy.1.2")), med.d = map(data, ~getStat(., "Tajima.D_1")), med.e = map(data, ~getStat(., "Zeng.E_1")), med.h = map(data, ~getStat(., "Fay.Wu.H_1")), med.fst = map(data, ~getStat(., "Fst")), med.dxy = map(data, ~getStat(., "dxy.1.2"))) %>% select(-data) %>% unnest()

@@

MS6.1 = ms2b %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "iHS" = med.ihs) %>% select(sim_ploidy, DS, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, iHS) %>% group_by(sim_ploidy, DS) %>% summarize_all(c("CV", "lCV", "uCV"))

MS6.1 %>% melt(., id.var = c("sim_ploidy", "DS")) %>% separate(variable, c("variable","XX"), "_") %>% spread(XX, value) %>% filter(variable %in% c("-TajD", "Std.Fst", "iHS", "XPEHH")) %>% mutate(Variable = factor(variable, levels=c("-TajD", "Std.Fst", "iHS", "XPEHH"))) %>% ggplot(., aes(y = CV, fill = as.factor(DS), x = as.factor(sim_ploidy))) + geom_bar(stat="identity", position = position_dodge()) + geom_errorbar(aes(ymin = lCV, ymax = uCV, width = 0.5), position = position_dodge(width = 0.9)) + scale_fill_discrete(name = "Sampling", labels=c("Equal Individuals", "Equal Alleles")) + scale_y_continuous(labels=scaleFUN) + ylab("CV[MaxValue]") + xlab("Ploidy") + facet_wrap(~Variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_blank(), axis.title.y=element_text(size=16), axis.text.x=element_text(size=14), axis.title.x=element_text(size=16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

@@

#Recessive
kkk.1b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points.b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2b = kkk2 %>% filter(dom == 0.1 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Std.Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "IHS" = size.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

@@

#Combined AUC and MaxValue
kkk.3b %>% filter(variable %in% c("sim_ploidy", "sampGen", "-TajD", "Std.Fst", "IHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("-TajD", "Std.Fst", "IHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value, color = as.factor(sampGen)), shape = 18, position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ geom_point(data = kkk.med.points.b[kkk.med.points.b$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value), shape = 5, color = "black", position = position_dodge(width = 0.75), show.legend = F, size=2)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2"))+scale_color_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))

#Dominant
kkk.1c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue")

kkk.med.points.c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = med.d, "FayWuH" = med.h, "ZengsE" = med.e, "Std.Fst" = med.fst, "Dxy" = med.dxy, "XPEHH" = med.xp, "IHS" = med.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "MaxValue") %>% group_by(sim_ploidy, sampGen, variable) %>% summarize(value = median(value, na.rm=T))

kkk.2c = kkk2 %>% filter(dom == 0.9 & traj_ploidy == sim_ploidy & s == "0.01" & N=="10000" & driftGen == 0 & recomb == 1e-08)  %>% mutate("-TajD" = size.taj, "FayWuH" = size.h, "ZengsE" = size.e, "Std.Fst" = size.fst, "Dxy" = size.dxy, "XPEHH" = size.xp, "IHS" = size.ihs) %>% select(sim_ploidy, sampGen, `-TajD`, ZengsE, FayWuH, Std.Fst, Dxy, XPEHH, IHS) %>% melt(., id.var = c("sim_ploidy", "sampGen")) %>% mutate(stat = "AUC")

@@

#Combined AUC and MaxValue
kkk.3c %>% filter(variable %in% c("sim_ploidy", "sampGen", "-TajD", "Std.Fst", "IHS", "XPEHH") & stat == "AUC") %>% mutate(variable = factor(variable, levels = c("-TajD", "Std.Fst", "IHS", "XPEHH"))) %>% ggplot(., aes(y = value / 100000, fill = as.factor(sampGen), x = as.factor(sim_ploidy))) + geom_boxplot(outlier.shape = NA) + geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value, color = as.factor(sampGen)), shape = 18, position = position_dodge(width = 0.75), show.legend = F, size=2.5)+ geom_point(data = kkk.med.points.c[kkk.med.points.c$variable %in% c("-TajD", "Std.Fst", "IHS", "XPEHH"),], aes(y = value), shape = 5, color = "black", position = position_dodge(width = 0.75), show.legend = F, size=2)+ scale_fill_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2"))+scale_color_manual(name = "Generations\nsince Fixation", values = wes_palette("Royal2")) + scale_y_continuous(labels=scaleFUN) + ylab("Peak Area") + xlab("Ploidy") + facet_wrap(~variable, scales = "free", shrink = T, nrow = 1) + theme_bw() + theme(axis.text.y=element_text(size = 12), axis.title.y=element_text(size=16), axis.text.x=element_text(size=13), axis.title.x=element_text(size = 16), legend.text = element_text(size=13), legend.title = element_text(size=14), strip.text = element_text(size=14))
```

Supp Fig 6
```{r}

lCV <- function(data, N = 1000, n = 20){
    aa = foreach(i = 1:N, .combine = rbind) %do% {
      ndat = sample(data, n)
      sd(ndat, na.rm=T)/(mean(ndat, na.rm=T))*100}
    return(quantile(aa,0.05, na.rm=T))
}
